Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-22 vesicle_code/docs/permeableVes/main.tex
yny

The governing equations are non-dimensionalized by using a
characteristic length scale $R_0 = 10^{-6}$ m, a bending stiffness $k_b
= 10^{-19}$ J, and fluid viscosity $5 \times 10^{-2}$ kg/ms. We scale
time by $\tau\equiv\mu R_0^3/k_b = 0.5\;s$, the velocity by $R_0/\tau =
2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, tension by
$k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0/\mu = 10^{-3}$ m$^2$s/kg. Under this nondimensionalization, a two-dimensional
semipermeable vesicle in a viscous fluid is characterized by (a) its
reduced area $\alpha = 4\pi A/L^2 \in (0,1]$, where $L$ is the vesicle
length and $A$ is its area, and (b) its permeability $\beta =
k_w \mu /R_0$.  For a polyunsaturated PC bilayer
the hydraulic conductivity $k_w$ is in the range 
$10^{-14}\le k_w\le 10^{-12}$ m$^2$s/kg, and the corresponding range for $\beta$ is $10^{-11}\le \beta\le 10^{-9}$.

>>>>

The governing equations are non-dimensionalized by using a
characteristic length scale $R_0 = 10^{-6}$ m, a bending stiffness $k_b
= 10^{-19}$ J, and fluid viscosity $5 \times 10^{-2}$ kg/ms. We scale
time by $\tau\equiv\mu R_0^3/k_b = 0.5\;s$, the velocity by $R_0/\tau =
2\;\mu$m/s, the pressure by $k_b/R_0^3 = 10^{-1}$ Pa, tension by
$k_b/R_0^2 = 10^{-7}$ N/m, and the permeability by $R_0/\mu = 10^{-3}$ m$^2$s/kg. Under this nondimensionalization, a two-dimensional
semipermeable vesicle in a viscous fluid is characterized by (a) its
reduced area $\alpha = 4\pi A/L^2 \in (0,1]$, where $L$ is the vesicle
length and $A$ is its area, and (b) its permeability $\beta =
k_w \mu /R_0$.  
We convert the apparent permeability of 
a polyunsaturated PC bilayer  \cite{OlbrichRawiczNeedhamEtAl2000_BJ}
to the hydraulic conductivity $k_w$ using the conversion in \cite{FettiplaceHaydon1980_PhysRev}, and  found that 
$10^{-14}\le k_w\le 10^{-12}$ m$^2$s/kg, thus $\beta$ is  in the range $10^{-11}\le \beta\le 10^{-9}$.
